Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Turned on warnings in dir_create()
Updated global chunk settings

---
output:
  pdf_document:
    keep_tex: yes
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
options(kableExtra.auto_format = FALSE)

knitr::opts_chunk$set(echo = FALSE, 
                      include = FALSE,
                      dev = 'jpeg', 
                      fig.width = 8, 
                      fig.height = 6, 
                      message = FALSE
                      )
```

@@

if (!dir.exists("../figs_manuscript")) {
  dir.create("../figs_manuscript",
    showWarnings = FALSE
  )
}

>>>>

---
output:
  pdf_document:
    keep_tex: yes
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
# options(kableExtra.auto_format = FALSE,
#         knitr.table.format = "latex"
#         )

knitr::opts_chunk$set(echo = FALSE, 
                      include = FALSE,
                      # dev = 'jpeg', 
                      fig.width = 8, 
                      fig.height = 6, 
                      message = FALSE,
                      warning = FALSE,
                      cache = FALSE
                      )
```

@@

if (!dir.exists("../figs_manuscript")) {
  dir.create("../figs_manuscript",
    showWarnings = TRUE
  )
}
